A comparison of model-based and design-based approaches for spatial data.

### 2021-06-07 inst/SpatialDVM_Manuscript/SpatialDVM_Manuscript.Rmd
minor edit.

@@

<!-- \citep{Hansen1983evaluation, Brus1997random, VerHoef2002sampling, Cooper2006sampling, sterba2009alternative, Brus2020statistical, Chan2020bayesian} -->

sterba2009alternative: psychological context comparison, has a lot of the older background (e.g. Fisher, Neyman, etc.)

@@

There have been many comparisons between the two paradigms.......

>>>>

Several comparisons between the two paradigms have been made in many different contexts. @sterba2009alternative give psych context, old history fisher / Neyman

Many new methods have been constructed that combine aspects of both design-based and model-based approaches. Our goal is not to expand upon these methods nor is it to develop a novel method that combines the two approaches.

@@

: psychological context comparison, has a lot of the older background (e.g. Fisher, Neyman, etc.)

@@
